Data-driven Reduction of Multiscale Stochastic Dynamical Systems

### 2014-07-10 reducible_SDE/new_SDE/paper_outline.tex
added more to multiscale example

@@

Main message/contribution:
\begin{itemize}

\item

@@

\item Multiscale SDE setting

\item Analysis of NIVs (remark that applies to more general settings)

@@

@@

@@

>>>>

\section{Main message/contribution}

\item Link between data mining and dynamical systems

\item Doing slow variable reduction from SDEs using the Mahalanobis graph (using NIV for slow variable extraction)

\item We give a full mathematical analysis of the slow variable reduction/procedure, including necessary conditions and user configuration

@@

@@

\item Multiscale SDE setting: fast/slow, want to recover slow variable(s) even when the fast variables are large/very noisy

\item Background on NIVs

\item Error and estimation analysis of NIVs (remark that applies to more general settings): give conditions/bounds when we can recover the intrinsic slow variable

\item Empirical configuration/demonstration of the method, how to use the analysis to set the parameters in the algorithm

@@

\item Experimental results/demonstrations:
\begin{itemize}

\item DMAPS gives the fast, NIVs gives the slow

\item Illustration of different aspects (error terms) in the analysis

\item Show empirically what happens as we change the neighborhood (example from notes 1) (recovery of fast variable deep in the spectrum)

@@

We showed that in certain cases (when we do {\em not} have a simulator where we can change $\delta t$), the data cannot be processed as-is (we cannot find the right kernel scale given a fixed $\delta t$ such that we can accurately recover the slow variable).

@@

saturation time of SDE has to be smaller than the timescales

dmaps example: show we recover fast (or garbage), not slow variable
